Title Goes Here

### 2020-04-03 analysis/paper/paper.Rmd
computing CVs

#simpler way to calculate CV
sd(ML)/mean(ML)
```

@@

#simpler way to calculate CV
sd(ML)/mean(ML)

>>>>

#simpler way to calculate CV (%)
sd(ML)/mean(ML)*100
sd(BL)/mean(BL)*100
sd(TL)/mean(TL)*100
sd(SL)/mean(SL)*100
sd(MW)/mean(MW)*100
sd(TW)/mean(TW)*100
sd(SW)/mean(SW)*100

```
CV for all attributes are distributed from 23-31%

@@

# CV%
sd(ML)/mean(ML)*100
sd(BL)/mean(BL)*100
sd(TL)/mean(TL)*100
sd(SL)/mean(SL)*100
sd(MW)/mean(MW)*100
sd(TW)/mean(TW)*100
sd(SW)/mean(SW)*100

#CV ranges are 20-33% more broad...
```
